---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

Load the necesary libraries
```{r}
#Is necesary install before ggplo2
#install.packages("ggplot2")
library(ggplot2)
````

## Loading and preprocessing the data

Unzip the activity.zip file
```{r}
unzip("activity.zip")
```
Read de activy.csv file and show the head of the data
```{r}
data <- read.csv("activity.csv")
head(data)
```
## What is mean total number of steps taken per day?

1. Calculate the total number of steps taken per day and set the names of the data columns
```{r}
stepsByDay <- aggregate(data$steps, by=list(data$date), FUN=sum)
names(stepsByDay) <- c('date','steps')
```
2. Make a histogram of the total number of steps taken each day
```{r}
ggplot(data = stepsByDay, aes(x = date, y = steps)) +
geom_histogram(stat = "identity", fill="blue") +
theme(axis.text.x = element_text(angle = 90, size = 7))
```

3. Calculate the mean and the median of the total number of steps taken per day
```{r}
dataMean <- mean(stepsByDay$steps, na.rm = TRUE)
dataMedian <- median(stepsByDay$steps, na.rm = TRUE)
```
The mean is `r dataMean` and the median is `r dataMedian`.

## What is the average daily activity pattern?

1. Calculate the average of steps by 5-minute interval across all days.
```{r}
stepsByInterval <- aggregate(data$steps, by=list(data$interval), FUN=mean, na.rm = TRUE)
names(stepsByInterval) <- c('interval','meanSteps')

ggplot(stepsByInterval, aes(x=interval, y=meanSteps)) + geom_line() +
  xlab("5-minute intervals") + ylab("Average number of steps")
```

2. Find the 5-minute interval with the maximun average number of steps.
```{r}
maximun <- stepsByInterval[which.max(x = stepsByInterval$meanSteps), c('interval')]
```
The maximun average number of steps is in the 5-minute interval `r maximun`.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
